Classless Java

### 2015-10-15 paper/sections/Overview.tex
revising overview

\section{Overview}\label{sec:ep}

@@

>>>>

\section{Overview}\label{sec:ep}
The single inheritance support for classes in Java prohibits doing multiple
inheritance in Java. Instead, the support of multiple inheritance support for
interfaces makes us to think the possibility of using interfaces only, throwing
away classes. But immediately we will face the following three problems of using
interfaces in Java.

\subsection{Problems with Java Interfaces}\label{sec:intf_prob}
\paragraph{Instantiation Code}. If we use interfaces, then we cannot
avoid instantiation code. 
\begin{lstlisting}
interface P {
    default m() { ... }
}
\end{lstlisting}
For example, even if interface \texttt{P} is complete (does not contain any
un-implemented method), to instantiate it programmers still need to create a
class \texttt{PImpl} that has a constructor for instantiation:
\begin{lstlisting}
class PImpl extends P {}
\end{lstlisting}

\paragraph{Prohibition of Field Members Inside Interfaces}
Only methods (abstract, static or default) are allowed to appear in the
definition of interfaces. The use of interfaces prohibits defining field members
inside. This limitation of interfaces hinders the adoption of using interfaces
only. Because the need of using field members almost \emph{always} exists. Hence
it forces programmers to use classes, but this gives up the ability of multiple
inheritance in Java. So the trade-off is: if you use interfaces, then no field
members; if you use classes, then no multiple inheritance.

\paragraph{Manual Type Refinement}
We will introduce operations \texttt{with} and \texttt{clone}, which requires
return type refinement in extensions. A \texttt{clone} method
returns a copy of the current object. For example, interfaces \texttt{I} and its
extension \texttt{I2}:
\begin{lstlisting}
interface I { I clone(); }
interface I2 extends I { 
  // inherit I clone() from super-interface I
  // which should be refined to I2 clone();
  I2 clone();
}
\end{lstlisting}

Interface \texttt{I} contains a \texttt{clone()} method which returns a copy of
current object (of type \texttt{I}). Interface \texttt{I2} is an extension of
interface \texttt{I}, so inheriting the \texttt{clone()} method from
\texttt{I}. Since the current interface is \texttt{I2}, now the return type of
\texttt{clone()} \texttt{should} be refined to \texttt{I2}. However, interfaces
in Java does not provide this kind of automatic refinement. In order to achieve
the same effect, programmers have to manually override it by a new
\texttt{clone()} method with return type \texttt{I2}.

@@

In summary, our approach solves the three problems of interfaces
(Section~\ref{sec:intf_prob}):
\begin{itemize}
\item Instantiation Code: Our approach solves the instantiation problem by
  providing \texttt{of} methods, mimicking the behavior of constructors.
\item No Fields Inside Interfaces: In our approach, abstract methods without
  arguments stands for fields. The return type of the methods are the types of
  member fields. Getters and setters are also generated automatically.
\item Manual Type Refinement: The annotation processor is designed to do this
  type refinement automatically, for \texttt{with-} methods, \texttt{clone}
  methods, etc.
\end{itemize}
